---
title: "Introduction to steamR"
author: "steamR"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to steamR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
# Load the steamR package
library(steamR)
# Set your API key (replace with your actual key)
api_key <- "2E603E850E37D5636F36F229777BDB15"
# Example Steam ID for testing
steam_id <- "76561198105405940"
```

# Introduction

This vignette demonstrates how to use the **steamR** package (formerly known as SteamAPI) to retrieve data from the Steam API and visualize it. We will:

1.  Retrieve basic user summaries.
2.  Retrieve the list of owned games.
3.  Create a plot that visualizes playtime data for the owned games.

# Retrieve Data

## Get Player Summaries

```{r player-summaries, echo=TRUE}
player_info <- get_player_summaries(api_key, steam_id)
print(player_info)
```

## Get Owned Games

```{r owned-games, echo=TRUE}
owned_games <- get_owned_games(api_key, steam_id, include_appinfo = TRUE)
head(owned_games)
```

# Plotting Example: From Zero to Graph

In this section, we create a bar plot showing the total playtime (in hours) for each owned game.

```{r plot-owned-games, fig.width=7, fig.height=5, echo=TRUE}
if (!is.null(owned_games) && nrow(owned_games) > 0) {
  # Ensure the necessary columns are present; here we assume 'name' and 'playtime_forever'
  if("name" %in% names(owned_games) && "playtime_forever" %in% names(owned_games)) {
    # Convert playtime from minutes to hours
    owned_games$playtime_hours <- owned_games$playtime_forever / 60
    
    # Order games by playtime
    ordered_games <- owned_games[order(owned_games$playtime_hours, decreasing = TRUE), ]
    
    # Create a bar plot with game names on the x-axis and playtime (hours) on the y-axis
    barplot(ordered_games$playtime_hours,
            names.arg = ordered_games$name,
            las = 2,                 # rotate names for better readability
            col = "skyblue",
            main = "Playtime (Hours) for Owned Games",
            ylab = "Playtime (Hours)")
  } else {
    message("The owned games data does not have the expected columns ('name' and 'playtime_forever').")
  }
} else {
  message("No owned games data available to plot.")
}
```

# Conclusion

This vignette provided a quick tour of the **steamR** package:\
- Retrieving user and game data from the Steam API\
- Performing basic data wrangling\
- Creating a simple plot to visualize playtime data

For more information, please refer to the detailed documentation of each function.

